---
title: "Final Project"
author: '"Group #8: Terry Yu, Chuyue Cui, Caomengyu Xue, Zhuoning Zhang"'
date: "`r Sys.Date()`"
output:
  html_notebook: default
  word_document: default
  html_document: default
  pdf_document: default
urlcolor: blue
---

## 1. Introduction

In this analysis, we focus on Amazon and its role as a leading global e-commerce company. Amazon offers a variety of products across different categories, including consumer electronics, appliances, fashion, and more. The datasets used in this analysis provide insights into customer behavior and product listings on Amazon. The main problem addressed involves understanding customer preferences and identifying actionable strategies to improve product offerings and marketing tactics.

# First, set your working directory using setwd() and read in the data

First, setup the working directory and read in the problem data. The working directory is where the data input file and results output file are stored, together with this R mark down file. 

```{r}
# Set working directory
setwd("/Users/qiaobook/Desktop/Marketing w: R/Final Project")

# Load datasets
library(readxl)
products <- read.csv("/Users/qiaobook/Desktop/Marketing w: R/Final Project/Amazon-Products.csv")
customers <- read.csv("/Users/qiaobook/Desktop/Marketing w: R/Final Project/Amazon Customer Behavior Survey.csv")
```
Source Link: https://www.kaggle.com/datasets/swathiunnikrishnan/amazon-consumer-behaviour-dataset


## 2. Data Overview
- **Amazon Customer Behavior Survey Dataset**: This dataset captures customer survey responses, providing insights into customer preferences, purchasing behavior, and satisfaction levels.
- **Amazon Products Dataset**: This dataset contains detailed product information, including product names, categories, ratings, and pricing.

```{r}
# Load necessary libraries
library(tidyverse)
library(ggplot2)
library(wordcloud)
library(dplyr)
library(RColorBrewer)

# --- Data Cleaning for Products Dataset ---
products <- products %>%
  mutate(
    ratings = as.numeric(ratings), # Convert ratings to numeric
    discount_price = as.numeric(gsub("[₹,]", "", discount_price)), # Clean and convert prices
    actual_price = as.numeric(gsub("[₹,]", "", actual_price)), # Clean and convert prices
    discount_percent = ((actual_price - discount_price) / actual_price) * 100 # Calculate discount
  ) %>%
  filter(!is.na(ratings) & !is.na(discount_percent)) # Remove NA values

# --- Data Cleaning for Customer Survey Dataset ---
customers_cleaned <- customers %>%
  mutate(
    age = as.numeric(age), # Ensure age is numeric
    Purchase_Categories = as.character(Purchase_Categories), # Convert to character
    Purchase_Categories = strsplit(Purchase_Categories, ";") # Split multiple categories
  )

# --- One-Hot Encoding for Purchase Categories ---
# Split Purchase_Categories into multiple rows for easier analysis
customers_categories <- customers_cleaned %>%
  separate_rows(Purchase_Categories, sep = ";")  # Splits categories into individual rows

# --- Grouping Categories ---
# Define a mapping of categories to broader groups
# Comprehensive mapping of purchase categories
category_mapping <- c(
  # Personal Care
  "Beauty and Personal Care" = "Personal Care",
  "Skincare" = "Personal Care",
  "Hair Care" = "Personal Care",
  "Health and Wellness" = "Personal Care",
  "Fragrances" = "Personal Care",
  
  # Fashion
  "Clothing and Fashion" = "Fashion",
  "Footwear" = "Fashion",
  "Accessories" = "Fashion",
  "Jewelry" = "Fashion",
  "Watches" = "Fashion",
  
  # Food and Beverages
  "Groceries and Gourmet Food" = "Food & Beverages",
  "Snacks" = "Food & Beverages",
  "Beverages" = "Food & Beverages",
  "Alcohol" = "Food & Beverages",
  
  # Technology
  "Electronics" = "Technology",
  "Mobile Phones" = "Technology",
  "Laptops and Computers" = "Technology",
  "Wearable Tech" = "Technology",
  "Gaming Consoles" = "Technology",
  "Cameras" = "Technology",
  
  # Education and Media
  "Books" = "Education & Media",
  "Stationery" = "Education & Media",
  "Music" = "Education & Media",
  "Movies and TV Shows" = "Education & Media",
  "Educational Supplies" = "Education & Media",
  
  # Home and Living
  "Home and Kitchen" = "Home & Living",
  "Furniture" = "Home & Living",
  "Bedding" = "Home & Living",
  "Decor" = "Home & Living",
  "Lighting" = "Home & Living",
  
  # Sports and Fitness
  "Sports and Outdoors" = "Sports",
  "Fitness Equipment" = "Sports",
  "Outdoor Gear" = "Sports",
  "Athletic Apparel" = "Sports",
  
  # Baby and Kids
  "Baby Products" = "Baby & Kids",
  "Toys and Games" = "Baby & Kids",
  "Kids' Clothing" = "Baby & Kids",
  
  # Automotive
  "Car Accessories" = "Automotive",
  "Motorcycle Accessories" = "Automotive",
  "Tires" = "Automotive",
  "Car Electronics" = "Automotive",
  
  # Other
  "Pet Supplies" = "Other",
  "Industrial and Scientific" = "Other",
  "Tools and Home Improvement" = "Other",
  "Unknown" = "Other"
)

# Apply the mapping to reduce categories
customers_categories_grouped <- customers_categories %>%
  mutate(
    Grouped_Categories = recode(Purchase_Categories, !!!category_mapping, .default = "Other")
  )


# --- Summary Statistics ---
# Function to count missing values in each column
count_missing_values <- function(data) {
  sapply(data, function(column) sum(is.na(column)))
}

#We did an output of the missing values of the customer dataset as well but due to the sheer size and there being no missing values we omitted the function out, furthermore there is now no longer any missing values in the products dataset as we dropped columns with missing ratings as ratings is an integral part of our analysis-we thought of filling it in with the average ratings but it wouldn't be fair to the actual product in the context of this project. 

#Summary Function
summary(products)
#We omitted out the summary of customers due to the sheer volume of the dataset 

# --- Visualizations ---
# 1. Distribution of Ratings
ggplot(products, aes(x = ratings)) +
  geom_histogram(binwidth = 0.5, fill = "skyblue", color = "black") +
  labs(title = "Distribution of Product Ratings", x = "Ratings", y = "Frequency")

# 2. Calculate proportions for grouped categories
category_distribution <- customers_categories_grouped %>%
  count(Grouped_Categories) %>%
  mutate(proportion = n / sum(n))

#Pie chart
ggplot(category_distribution, aes(x = "", y = proportion, fill = Grouped_Categories)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(
    title = "Distribution of Customer Purchase Categories",
    x = NULL,
    y = NULL,
    fill = "Category"
  ) +
  theme_void() +  
  theme(legend.title = element_text(size = 12),
        legend.text = element_text(size = 10))

# Create the bar chart
# Summarize category counts
category_counts <- products %>%
  count(main_category) %>%
  mutate(percentage = n / sum(n) * 100)

ggplot(category_counts, aes(x = reorder(main_category, percentage), y = percentage, fill = main_category)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Distribution of Product Categories",
    x = "Category",
    y = "Percentage",
    fill = "Category"
  ) +
  scale_fill_viridis_d(option = "plasma") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
    ) +
  geom_text(aes(label = paste0(round(percentage, 1), "%")), vjust = -0.5) 

# 4. Shopping Satisfaction by Gender
ggplot(customers, aes(x = Gender, fill = as.factor(Shopping_Satisfaction))) +
  geom_bar(position = "dodge") +
  labs(title = "Shopping Satisfaction by Gender", x = "Gender", y = "Count", fill = "Satisfaction")

# 5. Browsing Frequency
ggplot(customers, aes(x = Browsing_Frequency)) +
  geom_bar(fill = "lightblue") +
  labs(title = "Browsing Frequency", x = "Frequency", y = "Count")

```
# Analysis:
Based on on our initial EDA, we can gain a good high level overview of the datasets. Due to the datasets being in direct relation with one another (One being the information about the product on Amazon and another being a customers responses and opinions towards their purchases), we can infer the interpretation of one dataset's segment to be in direct correlation to another as they must be used together to form a comprehensive analysis of customer behavior towards product categories.  
  
For our "Products" dataset we can see a more robust visualization of all product categories within the dataset, furthermore there is a clear purchasing emphasis on fashion & clothing items as evident by the chart. Afterwards the next most popular category seems to be items that fall under the appliances and electronics category and then followed by beauty & skincare products. 
  
For our "Customers" dataset we actually had to encode and remap the categories due to the unstructured nature of the dataset alongside the messy information pertaining to each category within the original dataset. However, after our cleaning we can see a similar pattern to the "Products" dataset, with individuals seemingly making the bulk of their listed purchases on fashion items and personal care products. Although unshown, it's valid to believe a good portion of the "others" category contains electronics as well when considered in relation to the "Products" piechart. 
  
Continuing onwards in terms of insights, we can infer a clear popularity in online shopping by women vs their male counterparts as evident by the distribution of the bar chart. Furthermore, we now know that the bulk of online shoppers aren't chronically online-with the bulk of customers browsing only a couple times per week followed by those that do so only a few times a month as these two groups far overshadow those that rarely shop online or do so on a daily basis (in terms of browsing).  
  
Finally, we can see that the overall rating of purchases is positive, with a score of 4 being the average. It's fair to assume that less products achieve the desired rating of "excellent" as the next highest distribution is that of a 3.5 with the remainder being above the 4 score average. 
  
All in all we can derive a good amount of insight from our initial EDA. We can infer our average consumer base to be a female that shops occasionally every week for clothing or personal use items that leave them feeling overall relatively satisfied! 


## 3. Problem Identification
# Overarching Question:
How can we analyze the performance of different product categories to identify and boost sales for lower-performing categories, while determining the primary consumer demographics associated with these categories for more targeted marketing strategies?
#Sub-Questions for a Deeper Analysis:
1.Who are the primary consumer demographics associated with each category? Is there a direct correlation between certain demographic variables and consumerism of certain product categories? If so, we can fine tune our marketing strategies for said demographic to further increase marketability for said demographic or potentially shift our focus in marketing to weaker demographics to increase their incentive to consume. 
2.Is there a correlation between a product’s rating and their discounted price; for example if a products rating is high does that mean it gets discounted less or the discounted price isn’t as big in comparison to the original price since it doesn’t need discounts to sell. This can then be tied to the customer satisfaction/review categorical columns to gain a deeper understanding of the impact of ratings and reviews on a products performance which should prove beneficial to our marketing strategy optimization 
3.*Sentiment Analysis of Customer Feedback*

#1 EDA: Consumer Demographics vs Purchase Categories
```{r}
category_demographics_grouped <- customers_categories_grouped %>%
  group_by(Grouped_Categories, Gender) %>%
  summarise(
    count = n(),
    avg_age = mean(age, na.rm = TRUE)
  ) %>%
  arrange(desc(count))

print(category_demographics_grouped)

# --- Visualization: Grouped Categories ---
ggplot(customers_categories_grouped, aes(x = Grouped_Categories, fill = Gender)) +
  geom_bar(position = "dodge") +
  labs(
    title = "Grouped Purchase Categories by Gender",
    x = "Grouped Categories",
    y = "Count",
    fill = "Gender"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Create age groups using ntile and prepare the data
customers_categories_grouped <- customers_categories_grouped %>%
  mutate(age_group = ntile(age, 4))  # Divide ages into 4 groups

age_category_data <- customers_categories_grouped %>%
  select(age_group, Grouped_Categories) %>%
  filter(Grouped_Categories != "Other") %>%  # Exclude "Other" category
  group_by(age_group, Grouped_Categories) %>%
  summarise(count = n(), .groups = "drop")  # Count occurrences per group

# Plot the word cloud for all categories per age group
par(mfrow = c(2, 2), mar = c(1, 1, 2, 1))  # 2x2 layout for age groups

for (age_group in unique(age_category_data$age_group)) {
  # Filter the data for the specific age group
  age_data <- age_category_data %>% filter(age_group == age_group)
  
  # Generate the word cloud
  wordcloud(
    words = age_data$Grouped_Categories,
    freq = age_data$count,
    scale = c(2, 0.8),  # Adjust the word size scale
    min.freq = 1, 
    max.words = 50,  # Display up to 50 categories
    colors = brewer.pal(8, "Set3"),
    random.order = FALSE
  )
  
  # Add a title for the age group
  title(main = paste("Age Group:", age_group), cex.main = 1.2)
}

# --- Correlation Analysis: Demographics and Categories ---
# Create a contingency table for Gender and Categories
gender_category_table <- table(customers_categories_grouped$Gender, customers_categories_grouped$Grouped_Categories)

# Chi-squared test to check correlation between Gender and Categories
chi_squared_result <- chisq.test(gender_category_table)
print(chi_squared_result)

# Correlation between Age and Purchased Categories
age_correlation <- customers_cleaned %>%
  mutate(category_count = str_count(Purchase_Categories, ";") + 1)  # Count number of categories per customer

correlation_age_categories <- cor(age_correlation$age, age_correlation$category_count, use = "complete.obs")
print(paste("Correlation between Age and Purchased Categories:", correlation_age_categories))
```
# Analysis
Based on sub EDA, we can see that the notion of females being the primary consumer lies true. Furthermore, the analysis unveils the two most common categories of purchase again to be "Fashion" and "Others" which encapsulates a lot of electronics and general use items. Additionally, we can see a deeper coverage of the consumer demographic with the most common age of female consumers to be 29.85 (30) and male consumers being 32, pushing the inference of most online consumers being in their early-mid adulthood. 
  
Finally, based on our chi-square test, we can conclude the following: demographic factors like age and gender have limited predictive power for consumerism in the dataset. This insight suggests that while demographics may be useful for basic segmentation, the key to boosting sales for lower-performing categories may lie in a deeper understanding of consumer interests, product relevance, and behavioral patterns beyond demographic profiles.

#2 EDA: Product's Rating vs It's Discounts
```{r}
# Summary statistics
summary(products$ratings)
summary(products$discount_percent)

# Discounts by Ratings
# Use a sample of the dataset to reduce clutter
set.seed(123)  # For reproducibility
sample_size <- 1000  # Choose an appropriate sample size
sampled_data <- products %>% sample_n(sample_size)

# Plot using the sampled dataset
ggplot(sampled_data, aes(x = discount_percent, y = ratings)) +
  geom_point(alpha = 0.6, color = "blue") +  # Add transparency for overlapping points
  geom_smooth(method = "lm", color = "red", se = FALSE) +  # Add trendline
  labs(
    title = "Discount Percentage vs. Ratings (Sampled Data)",
    x = "Discount Percentage (%)",
    y = "Ratings"
  ) +
  theme_minimal()  # Use a cleaner theme for readability

# --- Correlation Analysis ---
# Correlation between Ratings and Discounts
cor(products$ratings, products$discount_percent, use = "complete.obs")
```
# Analysis.  
  
Based on our sub EDA, we can actually see a very faint, negative correlation between a product's rating and it's discounted price. This in actuality does make sense as the lower a product performs/rates, the less people will buy of it, resulting in the need to drop prices to increase sales. 
  
#Sentiment Analysis of Customer Reviews
```{r}
library(tidytext)
feedback_data <- customers_categories_grouped %>%
  select(age_group, Grouped_Categories, Cart_Abandonment_Factors, Service_Appreciation, Improvement_Areas) %>%
  pivot_longer(cols = c(Cart_Abandonment_Factors, Service_Appreciation, Improvement_Areas),
               names_to = "Feedback_Type", values_to = "Feedback_Text") %>%
  filter(!is.na(Feedback_Text))  # Remove rows with missing feedback

# Tokenize and preprocess text data
tidy_feedback <- feedback_data %>%
  unnest_tokens(word, Feedback_Text) %>%
  anti_join(stop_words)  # Remove stopwords

# Sentiment Analysis using Bing Lexicon
feedback_sentiments <- tidy_feedback %>%
  inner_join(get_sentiments("bing")) %>%
  group_by(Feedback_Type, Grouped_Categories, sentiment) %>%
  summarise(count = n(), .groups = "drop") %>%
  spread(sentiment, count, fill = 0) %>%
  mutate(sentiment_score = positive - negative)

# Visualize Sentiment Scores by Feedback Type
ggplot(feedback_sentiments, aes(x = reorder(Grouped_Categories, sentiment_score), y = sentiment_score, fill = Feedback_Type)) +
  geom_col(position = "dodge") +
  coord_flip() +
  labs(title = "Sentiment Scores by Feedback Type and Product Category",
       x = "Product Category", y = "Sentiment Score", fill = "Feedback Type") +
  theme_minimal()

# Word Cloud for Feedback Themes
tidy_feedback %>%
  count(Feedback_Type, word, sort = TRUE) %>%
  group_by(Feedback_Type) %>%
  top_n(50, n) %>%
  ungroup() %>%
  with(wordcloud(word, n, max.words = 50, colors = brewer.pal(8, "Dark2")))
```
Our sentiment analysis chart provides a breakdown of sentiment scores for various product categories based on two feedback types: Improvement Areas and Service Appreciation. A positive sentiment score indicates favorable feedback, while a negative score highlights areas of dissatisfaction. From our chart we can see a Dominance of the “Other” category alongside strong performances in the "Personal Care and Fashion" categories. Additionally, we also included a word cloud to showcase the most commonly used words in the consumer feedback, allowing us to make an inference on the key reasons for customer's returning/cancelling their product order. 

## 4. Approach & Techniques Utilized 
To ensure our datasets were suitable for analysis, we employed a systematic data cleaning process. First missing values in important numerical columns such as "rating" was dropped as to maintain the dataset’s overall integrity for analysis. For textual columns, missing values were either excluded or labeled as "Unknown" to provide a placeholder without skewing results. Text data, such as product categories and feedback responses, were converted to lowercase and stripped of punctuation and stopwords to prepare for tokenization in sentiment analysis. Fields with multiple categories (e.g., Purchase_Categories) separated by semicolons were also split into individual rows to facilitate meaningful grouping and an accurate analysis, allowing each category to be analyzed independently, providing granular insights.

The two datasets, Amazon Products and Customer Behavior Survey, were also initially merged based on their shared field of product categories. This merging step would enable the linkage of customer feedback and demographic information to product-specific details, creating a unified dataset for deeper analysis. However, after our merged result, we realize the dataset would be too large for a proper analysis (18gb size). Furthermore, we can connect insights between the two datasets due to their shared nature that work in tandem with one another. 

A comprehensive category mapping was employed for our customer dataset, grouping granular product categories into broader ones (ex: “Clothing and Fashion” and “Footwear” into “Fashion”), to help reduce clutter, improving visualization, and providing higher-level insights into product performance and customer behavior. Furthermore, the encoding and mapping of our dataset into its current format allowed for a far smoother time in regards to working with it. Additionally the reduction/generalization of our dataset resulted in a cleaner and more understable output in our analysis as well. 

A combination of descriptive, statistical, and text-based analysis techniques was employed to derive actionable insights. Exploratory Data Analysis (EDA) was used to identify general patterns, such as the distribution of purchase categories, customer demographics, and cart abandonment reasons. Visualization tools such as bar plots, pie charts, and word clouds were used to communicate these findings effectively. Sentiment analysis was applied to text columns like Service Appreciation, Improvement Areas, and Cart Abandonment Factors to extract positive and negative sentiment trends. The bing lexicon was employed to calculate sentiment scores, which were visualized across product categories and age groups. This technique was particularly useful in uncovering underlying customer emotions that influence purchase behavior or highlight areas needing improvement. Feedback and sentiment were further analyzed in relation to broader product categories (ex: “Fashion”, “Personal Care”) and customer demographics (age groups, gender), offering tailored insights into customer preferences and areas of dissatisfaction.

The reasoning behind these techniques stems from their ability to provide flexibility, clarity, and depth in the analysis. Grouping granular categories into broader groups made the analysis scalable and manageable, simplifying the process of deriving actionable recommendations. The combination of text and numerical analysis ensured the findings were both comprehensive and actionable, focusing on identifying areas for improvement in underperforming categories and emphasizing strengths in high-performing ones. Visualization tools like ggplot2 ensured the results were clearly presented, enhancing the interpretability of the analysis. By leveraging both datasets, the analysis provided a holistic view of customer behavior and product performance, making the findings more generalizable and actionable for targeted marketing strategies and sales improvement.

## 5. Model Assesment
To address the business problem of identifying and boosting sales for underperforming categories while tailoring marketing strategies to key consumer demographics, I used a combination of distinctly different techniques to ensure both depth and breadth in the analysis.

#1. Sentiment Analysis:

The first technique involved sentiment analysis, which provided qualitative insights into customer feedback. Using the bing lexicon, I assessed the sentiment polarity of textual data such as Improvement Areas, Service Appreciation, and Cart Abandonment Factors. Positive and negative sentiments were quantified into sentiment scores, allowing me to identify which product categories received the most favorable or unfavorable customer feedback. By linking these sentiment scores to broader categories (e.g., “Fashion,” “Personal Care”), I was able to pinpoint areas of dissatisfaction for targeted improvements and amplify attributes that drive customer satisfaction. For instance, categories like “Fashion” and “Personal Care” stood out for their positive sentiment, suggesting that these categories could benefit from enhanced marketing efforts emphasizing quality and service reliability. Conversely, negative sentiment in “Home & Living” highlighted potential opportunities to improve product durability or variety.

#2. Descriptive Statistical Analysis and Visualization:

The second technique focused on descriptive statistical analysis and visualization to explore purchasing patterns across product categories and demographics. By grouping purchase categories into broader classifications and analyzing them alongside customer demographics (e.g., age groups, gender), I identified the key drivers of purchase behavior. Techniques like bar plots, pie charts, and word clouds were instrumental in uncovering patterns and effectively communicating insights. For example, the analysis revealed that certain age groups had clear preferences for specific product categories, with younger demographics leaning towards “Fashion” and “Technology” while older groups showed interest in “Home & Living” and “Food & Beverages.” These insights enable targeted marketing strategies tailored to the preferences of each demographic group.

#Combined Insights from Techniques:

The combination of sentiment analysis and statistical techniques offered a holistic view of the data. Sentiment analysis added depth by capturing customer emotions and opinions, while statistical analysis provided the necessary breadth to quantify and visualize the relationships between product categories, purchasing behavior, and demographics. Together, these techniques highlighted opportunities to improve customer satisfaction and engagement, particularly for underperforming categories like “Home & Living” and “Food & Beverages.”

Finally, tying these insights together, the analysis demonstrated that “Fashion” and “Personal Care” were consistently high-performing categories with strong customer satisfaction. By amplifying the positive aspects of these categories through targeted marketing campaigns and addressing dissatisfaction in categories like “Home & Living,” the analysis provides a clear pathway to boosting overall sales and improving the customer experience. This approach ensures that the business problem is addressed comprehensively, combining actionable insights from both qualitative and quantitative techniques.

## 6. Conclusions & Recommendations
#Conclusions:  
  
The analysis revealed significant insights into product performance, customer behavior, and feedback patterns that provide a solid foundation for addressing the business problem. Sentiment analysis and demographic exploration highlighted key opportunities to boost sales for underperforming categories while leveraging strengths in high-performing ones.
	**1.	High-Performing Categories:**
	•	Categories like Fashion and Personal Care consistently scored high in sentiment analysis, with strong positive feedback in Service Appreciation. Customers appreciated aspects like product quality and delivery speed, making these categories ideal for further investment and marketing. These insights suggest that maintaining quality while amplifying strengths (e.g., user-friendly product descriptions or targeted promotions) can drive higher engagement and sales.
	**2.	Underperforming Categories:**
	•	Categories such as Home & Living and Food & Beverages exhibited mixed sentiment scores, particularly with notable dissatisfaction in Improvement Areas. Feedback included concerns about product quality, variety, and packaging. These issues likely contribute to lower performance and should be addressed to rebuild customer trust and increase sales.
	**3.	Customer Demographics:**
	•	Analysis of purchase patterns by age groups revealed distinct preferences. Younger age groups leaned towards categories like Fashion and Technology, while older demographics favored Home & Living and Food & Beverages. This demographic segmentation offers opportunities for tailored marketing strategies, ensuring that campaigns resonate with the right audience.
	**4.	Cart Abandonment:**
	•	The analysis of Cart Abandonment Factors identified recurring reasons such as high prices and unclear checkout processes. These factors are barriers to conversion and highlight areas where operational improvements can reduce friction and increase completed purchases.

#Recommendations:  
	**1.	Focus on High-Performing Categories:**
	•	For Fashion and Personal Care, invest in marketing campaigns that emphasize their strengths, such as quality, style, and customer satisfaction. Collaborations with influencers and loyalty programs could further boost engagement with younger demographics.
	**2.	Address Pain Points in Underperforming Categories:**
	•	For Home & Living and Food & Beverages, prioritize improvements in product quality and variety. Customer feedback on Improvement Areas suggests enhancing packaging and durability. Running limited-time promotions or offering satisfaction guarantees may also help rebuild customer confidence.
	**3.	Tailor Marketing Strategies by Demographics:**
	•	Develop age-specific campaigns to match customer preferences. For younger audiences, emphasize innovation and style in Fashion and Technology products. For older demographics, highlight practicality, durability, and value in Home & Living and Food & Beverages.
	**4.	Streamline the Purchase Process:**
	•	Reduce cart abandonment by addressing factors such as high prices and checkout friction. Implement transparent pricing, simplify checkout flows, and introduce discount codes or free shipping incentives to improve the conversion rate.
	**5.	Reclassify the “Other” Category:**
	•	The “Other” category significantly skewed sentiment results, masking actionable insights. Reclassify these products into specific categories where possible to better capture customer feedback and improve the granularity of future analyses.

#Final Thoughts:  
  
By combining customer sentiment insights with demographic trends, this analysis offers a roadmap for optimizing product performance and enhancing customer satisfaction. Addressing pain points in underperforming categories and tailoring strategies to customer preferences will not only boost sales but also foster long-term loyalty and engagement.
